---
title: "A Note on Cooperation in Repeated Games: Kreps et al.'s model"
author: "Andrea Guido"
date: 2020-05-02
categories: ["R"]
tags: ["Cooperation", "Game Theory"]
---

While reading Kreps et al.'s 1982 (JET) paper, I started to wonder what the model predictions look like when pluggin in some values into equations.

The model shows how coopearation can be rational in repeated PD games, assuming the presence of particular informational asymmetries, for example, concerning the type of a player (rational vs. TFTer).

Let's set up the model parameters (see the paper for their interpretation). I setup two possible scenarios by assigning different values to parameters. We will see later the purpose of this.

```{r setup}
# Payoffs - Scenario 1
a = 2
b = -1
# Probability q and number of rounds
q = seq(0, to = 1, by = .1)
N = 30
```

Let's now compute the threshold round before which ROW plays TFT with certainty.

```{r threshold}
n_star = 1+(2*a - 4*b +2*q)/q
```

Let's plot it!
```{r plot 1}
plot(q, n_star, type = "l", col="red")
```


Let's consider an alternative scenario, by considering an unit increase (decrease) in a (b).

```{r setup2}
# Payoffs - Scenario 2
a2 = 3
b2 = -2
n_star_2 = 1+(2*a2 - 4*b2 +2*q)/q
```

and plot the results:
```{r line}
plot(q, n_star, type = "l", col="red")
lines(q, n_star_2, col= "blue")
abline(h=N)
legend(x=.4,y=80, legend = c("2;-1", "3;-2"), fill = c("red", "blue"),  horiz = T)
```

Let's now see what it looks like in terms of number of rounds in which both players cooperate
```{r number coop}
Round_coop= N- n_star
Round_coop2=N-n_star_2
plot(q, Round_coop, type = "l", col="red")
lines(q, Round_coop2, col= "blue")
legend(x=.4,y=-30, legend = c("2;-1", "3;-2"), fill = c("red", "blue"),  horiz = T)
abline(h=0)
```